{\Huge Introduction and Related work}

### 2017-12-13 paper/paper.tex

    A Bittorrent client application listens to a specific port in every machine. To be able to add this port to the NAT in its router, one must use \textbf{universal plug in play (UPnP)} to avoid manually adding a port and a ip address to the NAT. The UPNP is a way to configure the NAT in any programming language. Telling the router which computer to forward a connection to is called \textbf{port forwarding}, each server based application has a port number it works through, its port number is very useful in giving the router the information it needs to forward a connection.

>>>>

    A Bittorrent client application listens to a specific port in every machine. To be able to add this port to the NAT in its router, one must use \textbf{universal plug in play (UPnP)} to avoid manually adding a port and a IP address to the NAT. The UPNP is a way to configure the NAT in any programming language. Telling the router which computer to forward a connection to is called \textbf{port forwarding}, each server based application has a port number it works through, its port number is very useful in giving the router the information it needs to forward a connection.
